### 2015-10-03 MSteenhagen-CV.tex
Updated date
New CV added

\documentclass[11pt]{article}

@@

%% Change as needed. Or just add me as a coauthor. Only some of these are 
%% used below in the hyperref declaration and address banner section.
\def\myauthor{Maarten Steenhagen}
\def\mytitle{Vita}
\def\mycopyright{\myauthor}
\def\mykeywords{}
\def\mybibliostyle{plain}
\def\mybibliocommand{}
\def\mysubtitle{}
\def\myaffiliation{University College London}
\def\myaddress{Department of Philosophy}
\def\myemail{m.steenhagen.09@ucl.ac.uk}
\def\myweb{http://ucl.ac.uk/\string~uctymst}
\def\myblog{http://maarten.steenhagen.nl}
\def\myphone{+44 (0)777 1193717}
\def\myfax{~}
\def\myversion{}
\def\myrevision{}

\def\myaffiliation{University College London}
\def\myauthor{Maarten Steenhagen}
\date{} % not used (revision control instead)
\def\mykeywords{Maarten, Steenhagen, Maarten Steenhagen, Vita, CV, Resume, Philosophy}

@@

%% needed for xelatex to work
\usepackage{fontspec}
\usepackage{xunicode}

%% color for the links 
\usepackage{color}
\definecolor{grey}{cmyk}{0,1,0,0.8}
%% hyperlinks
\usepackage[xetex, 
	colorlinks=true,
	urlcolor=grey,
	plainpages=false,
  	pdfpagelabels,
  	bookmarksnumbered,
  	pdftitle={\mytitle},
  	pagebackref,
  	pdfauthor={\myauthor},
  	pdfkeywords={\mykeywords}
  	]{hyperref}

@@

%%%------------------------------------------------------------------------
%%% Address and contact block
%%%------------------------------------------------------------------------
\begin{minipage}[t]{2.95in}
 \flushright {\footnotesize \href{http://ucl.ac.uk/philosophy}{Department of Philosophy} \\ University College London \\ Gower Street \\ \vspace{-0.05in} London, \textsc{wc1e 6bt}}

\end{minipage}
\hfill     
%\begin{minipage}[t]{0.0in}
% dummy (needed here)
%\end{minipage}
\hfill
\begin{minipage}[t]{1.7in}
  \flushright \footnotesize Phone: \myphone \\  
  {\scriptsize  \texttt{\href{mailto:\myemail}{\myemail}}} \\
  {\scriptsize  \texttt{\href{\myweb}{\myweb}}}
	{\scriptsize  \texttt{\href{\myblog}{\myblog}}}
\end{minipage}

\vfil

%% Name 
\noindent{\Large {\textsc{maarten steenhagen}}}
\reversemarginpar

@@

\ind Doctoral Candidate (PhD) in Philosophy, \emph{University College London \vspace{0.01in}}

\ind Dissertation on the perceptual nature of pictorial representation\\ Supervisor: Prof. Mark Eli Kalderon\\Projected submission: Autumn 2014

@@

\ind Philosophy of psychology; Philosophy of perception; Aesthetics

@@

\ind Metaphysics; Metaethics; History of 20$^{\textrm{\tiny{th}}}$ c. philosophy; Philosophy of language

\bigskip
\bigskip
\vfil 
\marginhead{Education}

@@

\ind 2011. MPhil Stud., Philosophy. Dissertation: \href{http://discovery.ucl.ac.uk/1348204/}{\emph{The Collective Image}}. \emph{University College London, Department of  Philosophy \vspace{0.01in}}\\ Supervisors: Prof. Mark Eli Kalderon; Prof. Christopher Peacocke. \vspace{-0.1in}

@@

@@

\ind 2013. \href{http://www.ucl.ac.uk/ah/figs/homepage}{UCL Faculty of Arts and Humanities} Postgraduate Research Studentship. %(£36.000)

\ind 2011. \href{http://www.british-aesthetics.org}{British Society of Aesthetics} Two-year PhD Studentship Award. %(£36.000)

@@

%\newpage
%% Presentations
\marginhead{{\vskip 0.4em}Research \newline presentations \newline(recent)}
\medskip

\ind 2013. ``Response to Renault--Steele'' American Society of Aesthetics annual conference, Department of Philosophy, University of California at San Diego. (Invited response.)

@@

% \ind 2010. ``Photography and dull causation: Response to Atencia-Linares.'' University College London, 2010 Graduate Conference in Philosophy. (Response paper.)
% 
% \ind 2010. ``Explaining the Ugly: Disharmony and Unrestrained Cognition in Kant.'' Institute of Philosophy, London-Berkeley Graduate Conference in Philosophy.

@@

% \marginhead{{\vskip 0.3em}Publications}
% \medskip
% 
% \ind  Steenhagen, M. 2010. `Explaining the Ugly,' \emph{Esthetica,} November.
% 
% \ind  Steenhagen, M. 2009. `Verwarring over lelijkheid,' \emph{Cimedart,} 39:2.
% 
% \ind  Steenhagen, M. 2008. `De keerzijde van liefde,' \emph{Cimedart,} 38:3.
% 
% \bigskip

\marginhead{{\vskip 0.9em}Work \newline experience}
\medskip

@@

\ind 2012--Present. Editor of the \href{http:\\www.pjaesthetics.org}{\emph{Postgraduate Journal of Aesthetics.}}

@@

\ind 2010--Present. Co-organiser \href{http:\\www.londonaestheticsforum.org}{London Aesthetics Forum}, Institute of Philosophy, London.

\ind 2009--Present. Research assistant in Philosophy at Heythrop College London. Working on philosophy of psychology, clinical methodology and psychoanalysis.

@@

>>>>

\documentclass[12pt]{article}

@@

%% Change as needed. Or just add me as a coauthor. Only some of these are 
%% used below in the hyperref declaration and address banner section.
\def\myauthor{Maarten Steenhagen}
\def\mytitle{Vita}
\def\mycopyright{\myauthor}
\def\mykeywords{}
\def\mybibliostyle{plain}
\def\mybibliocommand{}
\def\mysubtitle{}
\def\myaffiliation{University of Antwerp}
\def\myaddress{Centre for Philosophical Psychology}
\def\myemail{maartensteenhagen@gmail.com}
\def\myweb{http://msteenhagen.github.io}
\def\myblog{http://maarten.steenhagen.nl}
\def\myphone{+44 (0)78 66 425161}
\def\myfax{~}
\def\myversion{}
\def\myrevision{}

% \def\myaffiliation{University of Antwerp}
\def\myauthor{Maarten Steenhagen}
\date{} % not used (revision control instead)
\def\mykeywords{Maarten, Steenhagen, Maarten Steenhagen, Vita, CV, Resume, Philosophy}

@@

%% needed for xelatex to work
\usepackage{fontspec}
\usepackage{xunicode}
\usepackage{multicol}
%% color for the links 
\usepackage{color}
\definecolor{grey}{cmyk}{0,1,0,0.8}
%% hyperlinks
\usepackage[xetex, 
	colorlinks=true,
	urlcolor=grey,
	plainpages=false,
  	pdfpagelabels,
  	bookmarksnumbered,
  	pdftitle={\mytitle},
  	pagebackref,
  	pdfauthor={\myauthor},
  	pdfkeywords={\mykeywords}
  	]{hyperref}

@@

%%%------------------------------------------------------------------------
%%% Address and contact block
%%%------------------------------------------------------------------------
\begin{minipage}[t]{2.95in}
 \flushright {\footnotesize {Centre for Philosophical Psychology} \\ University of  Antwerp \\ Stadscampus \\ Lange Sint-Annastraat 7, S.S.208 \\ \vspace{-0.05in} 2000 Antwerp, Belgium}

\end{minipage}
\hfill     
%\begin{minipage}[t]{0.0in}
% dummy (needed here)
%\end{minipage}
\hfill
\begin{minipage}[t]{1.7in}
  \flushright \footnotesize Phone: \myphone \\  
  {\scriptsize  \texttt{\href{mailto:\myemail}{\myemail}}} \\
  {\scriptsize  \texttt{\href{\myweb}{\myweb}}}\\
	{\scriptsize  skype: \texttt{maartensteenhagen}}
\end{minipage}

\bigskip  
%% Name 
\noindent{\Large {\textsc{maarten steenhagen}}}
\reversemarginpar

@@

\ind Research Fellow\\
Centre for Philosophical Psychology\\
University of Antwerp

\vspace{0.01in}

@@

\ind Philosophy of perception; Philosophy of psychology; Aesthetics

@@

\ind Metaphysics; History of analytic philosophy; Philosophy of language

% \ind Supervisor: Prof. Mark Eli Kalderon
% 
% \ind Expected: Spring 2015
% 
% \bigskip
\bigskip
\bigskip

\marginhead{{\vskip 0.3em}Publications}
\medskip
% 
\ind (forthcoming) `Psycho-analysis, philosophy, and the pictorial arts' in: Lacewing, Gibbs, Steenhagen (eds.) \emph{The Oxford Handbook of Philosophy and Psychoanalysis}. Oxford University Press.

\ind (forthcoming) \emph{The Oxford Handbook of Philosophy and Psychoanalysis}. Oxford University Press. (Associate editor)

\ind  (forthcoming). `Review of Lambert Wiesing's \emph{Sehen Lassen},' in: \emph{British Journal of Aesthetics}. DOI: 10.1093/aesthj/ayu016

\ind  (2010). `Explaining the ugly: disharmony and unrestrained cognition in Kant' in: \emph{Esthetica} (November).

\bigskip
\marginhead{Education}

@@

\ind 2014-2015. Visiting Research Student in the Department of Philosophy at the University of Toronto. Advisor: Mohan Matthen.

\ind 2011-2015. Ph.D., Philosophy. Dissertation:
\emph{Appearance and Representation}. 
\emph{University College London, Department of  Philosophy \vspace{0.01in}}\\ Advisors: Prof. Mark Eli Kalderon; Prof. Mohan Matthen (Toronto)\\
Examiners: Prof. John Hyman (Oxford); Prof. David Papineau (KCL) 
\vspace{-0.1in}

\begin{quote}
	\textsc{abstract:} In this dissertation I examine the relation between two concepts that are indispensable both to the philosophy of perception and to philosophical aesthetics: appearance and representation. Either implicitly or explicitly, philosophers have disagreed over whether representations play any significant role in our perception of objects, events or properties. In this work I show that imagistic representations, such as photographs, paintings, and drawings, indeed play a significant part in our perception of the items we encounter in the world. My main claim is that such images fulfil a mediating function in vision, allowing us to perceive the scenes they represent by means of them. Images enable us visually to perceive scenes not present to the sense of sight, and in this way introduce into the world the possibility for a distinctive kind of visual appearance.
\end{quote}

\ind 2011. MPhil Stud., Philosophy. Dissertation: \href{http://discovery.ucl.ac.uk/1348204/}{\emph{The Collective Image}}. \emph{University College London, Department of  Philosophy \vspace{0.01in}}\\ Supervisors: Prof. Mark Eli Kalderon; Prof. Christopher Peacocke \vspace{-0.1in}

@@

% \marginhead{{\vskip 0.3em}Publications}
% \medskip
% %
% \ind (forthcoming) \emph{The Oxford Handbook of Philosophy and Psychoanalysis}. Oxford University Press. (Associate editor)
%
% \ind  (forthcoming). `Review of Lambert Wiesing's \emph{Sehen Lassen},' in: \emph{British Journal of Aesthetics}. DOI: 10.1093/aesthj/ayu016
%
% \ind  (2010). `Explaining the ugly: disharmony and unrestrained cognition in Kant' in: \emph{Esthetica} (November).
% 
% \ind  Steenhagen, M. 2009. `Verwarring over lelijkheid,' \emph{Cimedart,} 39:2.
% 
% \ind  Steenhagen, M. 2008. `De keerzijde van liefde,' \emph{Cimedart,} 38:3.
% 
% \bigskip

@@

\ind 2015. Jacobsen Studentship, Royal Institute of Philosophy, London (£9000).

\ind 2014. American Philosophical Association, Postgraduate bursary (\$400).

\ind 2013. \href{http://www.ucl.ac.uk/ah/figs/homepage}{UCL Faculty of Arts and Humanities} Postgraduate Research Studentship (£5000) %(£36.000)

\ind 2011. \href{http://www.british-aesthetics.org}{British Society of Aesthetics} Two-year PhD Studentship Award (£36.000).

@@

%\newpage
%% Presentations
\marginhead{{\vskip 0.4em}Talks \newline(recent)}
\medskip

\ind 2016. ``False reflections'' American Philosophical Association, Eastern Division Meeting, San Diego. (Upcoming)

\ind 2015. ``Collingwood, sympathy, and the work of art'' INSEI workshop on empathy and interpretation. Cambridge, UK

\ind 2014. ``Source representationalism'' Postgraduate Sessions of the Joint Session of the Aristotelian Society and Mind Association, University of Cambridge.

\ind 2014. ``Thoughts you don't think'' American Philosophical Association, Pacific Division Meeting, San Diego. Respondent: Dr. Katherine Rickus (Marquette)

% \ind 2013. ``Response to Renault--Steele'' American Society of Aesthetics annual conference, Department of Philosophy, University of California at San Diego. (Invited response.)

@@

% \ind 2010. ``Photography and dull causation: Response to Atencia-Linares.'' University College London, 2010 Graduate Conference in Philosophy. (Response paper.)

\ind 2010. ``Explaining the Ugly: Disharmony and Unrestrained Cognition in Kant.'' Institute of Philosophy, London-Berkeley Graduate Conference in Philosophy.

@@

\marginhead{{\vskip 0.9em}Professional \newline experience}
\medskip

\ind 2014--Present. Referee for \emph{British Journal of Aesthetics} and \emph{Topoi}.

@@

\ind 2012--2015. Editor of the \href{http:\\www.pjaesthetics.org}{\emph{Postgraduate Journal of Aesthetics.}}

@@

\ind 2010--2015. Co-organiser \href{http:\\www.londonaestheticsforum.org}{London Aesthetics Forum}, Institute of Philosophy, London.

\ind 2009--2015. Research assistant in Philosophy at Heythrop College London. Working on philosophy of psychology, clinical methodology and psychoanalysis.

@@

\ind Interdisciplinary Network on Sympathy, Empathy and Imagination (INSEI).
